An Inception Cohort Study Quantifying How Many Registered Studies are Published.

### 2023-06-18 paper.tex
minor changes

\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={An Inception Cohort Study Quantifying How Many Registered Studies are Published.},
  pdfauthor={Eline Ensinck1 \& Daniël Lakens1},
  pdflang={en-EN},
  pdfkeywords={File Drawer; Registries; Research Waste; Scientific Publication},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{An Inception Cohort Study Quantifying How Many Registered Studies are Published.}
\author{Eline Ensinck\textsuperscript{1} \& Daniël Lakens\textsuperscript{1}}
\date{}

@@

This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. The computationally reproducible version of this manuscript is available at \url{https://github.com/Lakens/registered_published} and additional materials on \url{https://osf.io/8uqfb/}. We would like the thanks Stephen Lindsay, Cristian Mesquida Caldentey, and Henry Wyneken for feedback on a draft.

@@

\abstract{%
We quantified how many studies registered on the Open Science Framework (OSF) up to November 2017 are performed but never shared. Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (62\%) were published. We estimate that 5550 out of 9544 (58\%) registrations on the OSF are published within at least 4 years. Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community. In responses to emails asking researchers why studies remained unpublished, logistical issues (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review. Our study shows that a substantial amount of data that researchers collect is never publicly shared.
}

@@

The most accurate estimates of the percentage of performed studies in the file drawer come from inception cohort studies where studies are -- typically retroactively - followed from the moment they are started (\protect\hyperlink{ref-song_dissemination_2010}{Song et al., 2010}). For example, Dickersin and colleagues observed that from all studies approved by two institutional review boards serving the school of medicine and the school of health at the John Hopkins University 81\% and 66\% were published, respectively (\protect\hyperlink{ref-dickersin_factors_1992}{Dickersin et al., 1992}). In the only inception cohort study in the social sciences we know of, Franco, Malhotra, and Simonovits (\protect\hyperlink{ref-franco_publication_2014}{2014}) found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45\%), 29\% of studies were written up but remained unpublished at the time of the study, and 20\% (primarily non-significant results) were unpublished and not written up.

One way to make all studies that have been performed known to peers is to require researchers to (pre)register their study in a publicly accessible database (\protect\hyperlink{ref-dickersin_evolution_2012}{Dickersin \& Rennie, 2012}). Registries often require researchers to update a registered study with the results. An example of such a study registry is ClinicalTrials.gov. The requirement to register certain types of studies does not exist in psychology. However, since 2013 the Open Science Framework (OSF) has provided a free study registry for any scientific domain (\protect\hyperlink{ref-spies_open_2013}{Spies, 2013}). The OSF offers researchers the possibility to voluntarily register their study by specifying their hypotheses, methods, and statistical analysis plan.

One interesting aspect of registrations on the OSF is the fact that every registration after June 8 2015 (if not withdrawn) will be made public after an embargo period of four years\footnote{see \url{https://web.archive.org/web/20230519110220/https://groups.google.com/g/openscienceframework/c/3ZaZYKV8WD4/m/JCN4OB31skQJ}}. This policy means that the OSF provides a public record of all studies that were registered on the platform up to four years ago. It is therefore possible to use the database of registered studies for an inception cohort study that quantifies how many studies are performed, but never publicly shared.

@@

Second, we were interested in whether a registry with the policy to make registration public after an embargo facilitates identifying unpublished studies. By comparing the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can answer two questions. How often do researchers voluntarily share information about their study, even when the study remains unpublished? And how often do we learn about performed but unpublished studies because of the OSF policy to automatically make registrations public after four years? Answers to these questions can provide insights into the benefits of a platform that makes registrations public after a certain time (e.g., OSF), compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).

Our third question concerns the possibility to correctly identify whether a registered study is publicly shared, or not. For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to match the registration to a published study, or to conclude the registered study remains unpublished. As far as we know, this is the first investigation that retrieves registrations from the OSF to attempt to identify whether the associated study has been publicly shared or not.

@@

\emph{Data sources}: As registrations become public after four years, we downloaded all information that can be retrieved through the application programming interface (API) of the OSF for 17.729 registrations that were created before November 18, 2017 (four years before the start of this study). Registrations are part of at least one associated project page on the OSF. Sometimes researchers still work on projects four years after a registration, and we saw continued activity in some registrations in our sample. The final classification was based on whether the projects were public in April 2022. For 8008 registrations (45.17\%) the associated project was public, while for the remaining 9721 registrations (54.83\%) the associated project was private. We randomly sampled registrations from both these groups. During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database). Our sampling strategy increased the probability that studies with multiple registrations were included in the study.

\emph{Classifying Registrations}: We aimed to examine at least 300 registrations (150 for which the registration was made public by the researchers, and 150 for which the registration was made public automatically after four years ). The OSF API does not provide information about how a project has been made public. To circumvent this limitation, we relied on a proxy indicator to classify projects as opened by the user, or opened automatically when the embargo was lifted. We classified OSF registrations as made public by the researcher when any of the associated OSF project pages was public, and classified the project as made public automatically by the OSF after four years when the associated project page was not made public. Our reasoning is that when only the registration is public, but the underlying project remains closed, the registration is most likely opened automatically, as there are not that many use-cases where a researcher would open the registration, but not the associated project. This is not a perfect proxy, as it is possible for users to make a registration public, but to keep the associated OSF project hidden (for example, because they mistakenly believe they made the entire project public when making the registration public). When the registration and underlying project are public, we assume the registration is opened by the researchers. This assumption is more likely to hold, as only users can make underlying project pages public.

\emph{Classifying Publication Status}: Studies can be available in different degrees, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal (\protect\hyperlink{ref-lishner_sorting_2021}{Lishner, 2021}). We considered a study `published' if the study was communicated in any form that allows other researchers to learn about the results. In the remainder of this article the term `published' is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis (see the online supplementary material for more detail). We did not include bachelor or master theses because even though these can eventually be published (as this article demonstrates) they primarily have an educational goal and we do not consider the file drawer problem equally applicable to this category of studies. Our definition of `published' is broader than in previous inception cohort studies (e.g., Dickersin et al. (\protect\hyperlink{ref-dickersin_factors_1992}{1992}); Franco et al. (\protect\hyperlink{ref-franco_publication_2014}{2014})). We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, especially because preprints provide a possible outlet for studies that a researcher might decide not to submit to a scientific journal.

@@

\emph{Identifying Publications Corresponding to Registrations}: We attempted to find a publication (e.g., a journal article, preprint, thesis, or scientific poster) associated with each registration included in the analysis. Ideally, it is possible to find a publication associated with a registration without the help of the researchers who performed the study. In practice, due to the often limited information included in a registration on the OSF, information provided by the researchers improved our ability to classify registrations as publicly shared or not. If a publication could be found that provided a direct link to the OSF registration we could be certain that we found the publication corresponding to the registration. In many cases, especially when registrations on the OSF contained little information, and publications did not link to a registration on the OSF, there was some uncertainty about whether a paper corresponded to a registration. Furthermore, if no publication could be found, there always remained the possibility that we failed to find it. Based on an extensive search (for details, see the online supplement) we classified 68 out of the 169 registrations as published, 71 registrations as unpublished, and for 30 registrations we were uncertain about whether the registration was published. We remained uncertain when, for example, there was very little information in the preregistration, and the information that was available seemed related to a paper without a link to an OSF registration.

For all registrations where we were uncertain about whether a publication corresponded to the registration, we attempted to retrieve contact information of researchers involved, and contacted the researchers. We also contacted researchers associated with all registrations classified after an extensive search as unpublished, to check if the registration was indeed unpublished, and if so, ask the researchers why the study remained unpublished. We contacted 109 researchers, 29 researchers with registrations associated with public OSF projects and 80 researchers with registrations associated with closed OSF projects, of which 24 (82.76\%) and 53 (66.25\%) replied to our email with additional information to update our classification. We sent one email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received one response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file-drawer (\protect\hyperlink{ref-van_elk_whats_2021}{van Elk, 2021}), 77 emails for registrations we believed remained unpublished (and received 51 responses), and 31 emails because we were uncertain if they were published or not (and received 25 responses). Two additional researchers replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.

After updating our classification based on email responses, the publication rate in group 1 increased by 6\% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1\%. Sometimes a publication we found in the literature did not belong to the registration. If the study associated with the registration was published in another source than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers. In total, 48 of the 76 responses match with publications we found. For the 50 registrations we classified as unpublished, responses to the follow-up emails indicated that 36 (72\%) were unpublished, while for 14 (28\%) we failed to identify the published paper based on the information in the registration. Most of the mismatches occurred when we were uncertain about whether a paper we found included the registered study because there was no link to the registration on the OSF and only some terminology in the registration and article overlapped. For the 25 registrations where we were uncertain if the study was published, 11 (44\%) of registrations matched a paper we found. Of the 14 (56\%) cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published. In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published. Altogether, these results indicate that without contacting the researchers it is often difficult to determine whether a registration is published based exclusively on the information researchers provide in their registration on the OSF.

Due to non-response to our emails there is remaining uncertainty about the number of registrations in our sample that were eventually published. The 26 non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the 6 non-responses related to registrations where we remained uncertain similarly contain some published and some unpublished studies. Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration. Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that 6.55 out of 26 registrations in the unpublished classification and 2.97 out of 6 registrations in the uncertain classification are actually published.

@@

After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response, we predict that out of a total of 169 included registrations, 103.52 registered studies are published (61.25\%, 95\% CI {[}53.74; 68.27{]}). Our sample intentionally contained an almost equal number of manually opened and automatically opened registrations. As can be seen in Table \ref{tab:table-estimated-nonpublication} manually opened registrations were much more likely to be published than automatically opened registrations, but also somewhat less frequent in the total population of registrations. Multiplying our publication estimates by the estimated number registrations on the OSF before November 2017 that can be classified as an actual research study we find that 5550 registrations are published, and 3994 remain unpublished. Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that 58.15\%, of registrations are published as an article, preprint, thesis, or poster after at least four years.

@@

We see that 85.91\%, 95\% CI {[}77.13; 91.68{]} of all registrations that based on our proxy were classified as manually opened by the researchers have been published. In the remaining 14.09\% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published. This shows that a platform that enables researchers to make their registration public will make studies that would otherwise remain in the file-drawer known to the research community. We estimate that 34.47\%, 95\% CI {[}25.04; 45.31{]} of automatically opened registrations is published. Consequently, 65.53\% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years. In other words, automatically opening registrations increases our awareness of all studies that have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.

@@

According to the responses we received, logistical issues are the biggest cause of unpublished studies in our sample. Researchers leave academia and fail to complete a project before their contract ends, move on to a new position with a different research focus, or experience a lack of time to complete this specific project given other responsibilities. In some of these cases researchers did intend to come back to this project, and we observed continuing activity in projects registered more than four years ago, including publications that appeared in the literature.

@@

When asked why researchers made their OSF project page open, most researchers (18 out of 23) mentioned a motivation to practice open science. Out of 43 responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information stored in the project (15 times), researchers forgot to open it (11 times), were waiting until a project was published (6 times), or experienced technical issues (4 times). For more details, see the online supplement. Finally, we were interested in how many researchers who registered on the OSF before 2017 - many of which should be considered early adopters - were aware of the OSF policy to automatically open all registrations after four years. Although not all of the email respondents answered this question, 24 of the researchers indicated they were aware of this policy, and 14 were not aware of this policy.

@@

Our examination of 169 registrations led to an estimated publication rate of 58.15\%, for all registrations on the Open Science framework that were created before November 18, 2017. Extrapolating from our sample to the population of all registrations up to November 2017 (for details, see the online supplement), we estimate that of the 9544 registered research studies on the OSF that met our inclusion criteria, 3994 remain unpublished. Our study provides an important datapoint to understand how many studies are performed, but never shared. The possibility that around 41.85\% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research. Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced (\protect\hyperlink{ref-bernal_social_1939}{Bernal, 1939}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}), wherever this waste is avoidable.

The main reason researchers give when asked why their studies remain unpublished are logistical issues related to a lack of time, or responsible researchers moving on to a new job. Better time-management, designing projects from the outset in a way that they can be completed by other team members, or making unfinished projects available to potential collaborators could mitigate these issues. The fact that for 25\% of unpublished studies researchers indicated that the reason that the study remained unpublished is due to the results (e.g., null results or failed replications) is concerning, and considered unacceptable by the general public (\protect\hyperlink{ref-bottesini_what_2022}{Bottesini, Rhemtulla, \& Vazire, 2022}; \protect\hyperlink{ref-pickett_questionable_2017}{Pickett \& Roche, 2017}). It is possible that the absence of these studies contributes to publication bias in the scientific literature. Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report (\protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-nosek_registered_2014}{Nosek \& Lakens, 2014}). If researchers do not report failed replications it is impossible to correct false positive claims in the scientific literature (\protect\hyperlink{ref-schmidt_shall_2009}{Schmidt, 2009}), and if null-results remain unreported effect size estimates in meta-analyses will be inflated (\protect\hyperlink{ref-egger_bias_1997}{Egger, Davey Smith, Schneider, \& Minder, 1997}).

Our estimate has remaining uncertainty as some registrations for which authors did not respond to our email might be classified incorrectly. Furthermore, the estimate is specific to the context of our study, which were all registrations on the OSF created before November 18, 2017. Users of the OSF in these years are early adopters interested in open science practices, and the likelihood they share a study might differ from researchers who do not use the OSF. Our estimate might not generalize to non-registered studies. The estimate might also change over time (e.g., more studies might have remained unpublished during the COVID pandemic). In short, the exact percentage of studies that remain unpublished will be different in other contexts.

At the same time, the factors that cause researchers not to publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts. In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, there might be less reason to be concerned about the number of unpublished studies. Our study demonstrates that the percentage of unpublished studies can be high. The question how many studies remain unpublished deserves attention across scientific contexts where similar factors preventing the publication of studies play a role. Empirically examining the size of the file drawer can determine if there is room for improvement.

>>>>

\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={An Inception Cohort Study Quantifying How Many Registered Studies are Published.},
  pdfauthor={Eline N. F. Ensinck1 \& Daniël Lakens1},
  pdflang={en-EN},
  pdfkeywords={File Drawer; Registries; Research Waste; Scientific Publication},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{An Inception Cohort Study Quantifying How Many Registered Studies are Published.}
\author{Eline N. F. Ensinck\textsuperscript{1} \& Daniël Lakens\textsuperscript{1}}
\date{}

@@

This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. A computationally reproducible manuscript is available at \url{https://github.com/Lakens/registered_published} and data and materials on \url{https://osf.io/8uqfb/}. We are grateful to Stephen Lindsay, Cristian Mesquida Caldentey, Henry Wyneken, and Gerda Wyssen for feedback on a draft.

@@

\abstract{%
We quantified how many studies registered on the Open Science Framework (OSF) up to November 2017 are performed but not shared after at least 4 years. Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (61.3\%) were published. We estimate that 5550 out of 9544 (58.2\%) registered studies on the OSF are published. Researchers use registries to make unpublished studies public, and the OSF policy to open registrations after a four year embargo substantially increases the number of studies that become known to the scientific community. In responses to emails asking researchers why studies remained unpublished logistical issues (e.g., lack of time, researchers changing jobs) were the most common cause, followed by null results, and rejections during peer review. Our study shows that a substantial amount of studies researchers perform remain unpublished.
}

@@

The most accurate estimates of the percentage of performed studies in the file drawer come from inception cohort studies where studies are -- typically retroactively - followed from the moment they are started (\protect\hyperlink{ref-song_dissemination_2010}{Song et al., 2010}). For example, Dickersin and colleagues observed that from all studies approved by two institutional review boards serving the school of medicine and the school of health at the John Hopkins University 81\% and 66\% were published, respectively (\protect\hyperlink{ref-dickersin_factors_1992}{Dickersin et al., 1992}). In the only inception cohort study in the social sciences we know of, Franco, Malhotra, and Simonovits (\protect\hyperlink{ref-franco_publication_2014}{2014}) found that out of 249 large studies on nationally representative samples 45\% were published in a scientific journal or as a book chapter, 29\% were written up but remained unpublished at the time of the study, and 20\% (primarily non-significant results) were unpublished and not written up.

One way to make all studies that have been performed known to peers is to require researchers to (pre)register their study in a publicly accessible database (\protect\hyperlink{ref-dickersin_evolution_2012}{Dickersin \& Rennie, 2012}). Registries often require researchers to update a registered study with the results. An example of such a study registry is ClinicalTrials.gov. The requirement to register certain types of studies does not exist in psychology. However, since 2013 the Open Science Framework (OSF) has provided a free study registry for any scientific domain (\protect\hyperlink{ref-spies_open_2013}{Spies, 2013}). The OSF offers researchers the possibility to voluntarily register their study and specify information about the study rationale and methods.

One interesting aspect of registrations on the OSF is the fact that every registration after June 8 2015 (if not withdrawn) is made public after an embargo period of four years\footnote{see \url{https://web.archive.org/web/20230519110220/https://groups.google.com/g/openscienceframework/c/3ZaZYKV8WD4/m/JCN4OB31skQJ}}. Because of this policy the OSF provides a public record of all studies that were registered on the platform up to four years ago. It is therefore possible to use the database of registrations for an inception cohort study that quantifies how many studies are performed, but never publicly shared.

@@

Second, we were interested in whether the policies of a study registry to automatically open registrations after an embargo increases the number of studies that become known to peers, compared to registries where registrations can remain closed indefinitely. By comparing the publication status of registrations that researchers manually made public with registrations automatically opened by the OSF we can answer two questions. How often do researchers voluntarily share information about their study, even when the study remains unpublished? And how often do we learn about performed but unpublished studies because registrations are automatically made public after four years? Answers to these questions can provide insights into the benefits of a platform that makes registrations public after an embargo period (e.g., OSF), compared to platforms where users can choose to make their registration public or not (e.g., AsPredicted.org).

Our third question examined whether fellow researchers can use registries to discover unpublished studies by identifying whether a registered study is publicly shared, or not. For a registry to notify the scientific community about the presence of unpublished studies the information in the registry needs to be extensive enough to match the registration to a published study, or to conclude the registered study remains unpublished. As far as we know, this is the first investigation that retrieves registrations from the OSF to attempt to identify whether the associated study has been publicly shared or not.

@@

\emph{Data sources}: As registrations become public after four years, we downloaded all information that can be retrieved through the application programming interface (API) of the OSF for 17.729 registrations that were created before November 18, 2017 (four years before the start of this study). Registrations are part of at least one associated project page on the OSF. Sometimes researchers still work on projects four years after a registration, and we saw continued activity in a few registrations in our sample. The final classification was based on whether the projects were public in April 2022. For 8008 registrations (45.17\%) the associated project was public, while for the remaining 9721 registrations (54.83\%) the associated project was private. We randomly sampled registrations from both these groups. During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database). Our sampling strategy increased the probability that studies with multiple registrations were included in the study.

\emph{Classifying Registrations}: We aimed to examine at least 300 registrations (150 for which the registration was made public by the researchers, and 150 for which the registration was made public automatically after four years). We had no justification for our sample size given uncertainty about the number of studies that would fit our inclusion criteria but relied on an informal trade-off between time constraints and sufficiently accurate estimates. The OSF API does not provide information about how a project has been made public. To circumvent this limitation, we relied on a proxy indicator to classify projects as opened by the user, or opened automatically when the embargo was lifted. We classified OSF registrations as made public by the researcher when any of the associated OSF project pages was public, and classified the project as made public automatically by the OSF after four years when the associated project page was not made public. Our reasoning is that when only the registration is public, but the underlying project remains closed, the registration is most likely opened automatically, as there are not that many use-cases where a researcher would open the registration, but not the associated project. This is not a perfect proxy, as it is possible for users to make a registration public, but to keep the associated OSF project hidden (for example, because they mistakenly believe they made the entire project public when making the registration public). When the registration and underlying project are public, we assume the registration is opened by the researchers. This assumption is more likely to hold, as only users can make underlying project pages public.

\emph{Classifying Publication Status}: Studies can be made available in different ways (\protect\hyperlink{ref-lishner_sorting_2021}{Lishner, 2021}). We considered a study published if the study was communicated in a way that allows other researchers to learn about the results. In the remainder of this article the term `published' is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis (see the online supplementary material for more detail). We did not include bachelor or master theses because even though these can eventually be published (as this article demonstrates) they primarily have an educational goal and we do not consider the file drawer problem equally applicable to this category of studies. Our definition of `published' is broader than in previous inception cohort studies (e.g., Dickersin et al. (\protect\hyperlink{ref-dickersin_factors_1992}{1992}); Franco et al. (\protect\hyperlink{ref-franco_publication_2014}{2014})). We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, and especially preprints provide a possible outlet for studies that a researcher might decide not to submit to a scientific journal.

@@

\emph{Identifying Publications Corresponding to Registrations}: We attempted to find a publication (e.g., a journal article, preprint, thesis, or scientific poster) associated with each registration included in the analysis. Ideally, it is possible to find a publication associated with a registration without the help of the researchers who performed the study. In practice, due to the often limited information included in a registration on the OSF, information provided by the researchers improved our ability to classify registrations as publicly shared or not. If a publication could be found that provided a direct link to the OSF we could be certain that we found the publication corresponding to the registration. In many cases, especially when registrations on the OSF contained little information (see the supplement for details on how much information registrations contained), and publications did not link to a registration on the OSF, there was some uncertainty about whether a paper corresponded to a registration. Furthermore, if no publication could be found, there always remained the possibility that we failed to find it. Based on an extensive search (for details, see the online supplement) we classified 68 out of the 169 registrations as published, 71 registrations as unpublished, and for 30 registrations we were uncertain about whether the registration was published. We remained uncertain when, for example, there was very little information in the preregistration, and the information that was available seemed related to a paper without a link to an OSF registration.

For all registrations where we were uncertain about whether a publication corresponded to the registration we attempted to retrieve contact information of researchers involved, and contacted the researchers. We also contacted researchers associated with all registrations classified after an extensive search as unpublished, to check if the registration was indeed unpublished, and if so, ask the researchers why the study remained unpublished. We contacted 109 researchers, 29 researchers with registrations associated with public OSF projects and 80 researchers with registrations associated with closed OSF projects, of which 24 (82.76\%) and 53 (66.25\%) replied to our questions with additional information to update our classification. We sent one email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received one response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file drawer (\protect\hyperlink{ref-van_elk_whats_2021}{van Elk, 2021}), 77 emails for registrations we believed remained unpublished (and received 51 responses), and 31 emails because we were uncertain if they were published or not (and received 25 responses). Two additional researchers replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.

After updating our classification based on responses the publication rate in group 1 increased by 6\% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1\%. Sometimes a publication we found in the literature did not belong to the registration. If the study associated with the registration was published in another source than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers. In total, 48 of the 76 responses matched with publications we found. For the 50 registrations we classified as unpublished, responses to the follow-up emails indicated that 36 (72\%) were unpublished, while for 14 (28\%) we failed to identify the published paper based on the information in the registration. Most of the mismatches occurred when we were uncertain about whether a paper we found included the registered study because there was no link to the registration on the OSF and only some terminology in the registration and article overlapped. For the 25 registrations where we were uncertain if the study was published, 11 (44\%) of registrations matched a paper we found. Of the 14 (56\%) cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published. In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published. Altogether, these results indicate that without contacting the researchers it is often difficult to determine whether a registration is published based exclusively on the information researchers provide in their registration on the OSF.

Due to non-response to our emails there is remaining uncertainty about the number of registrations in our sample that were eventually published. The 26 non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the 6 non-responses related to registrations where we remained uncertain similarly contain some published and some unpublished studies. Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration. Under this latter (more conservative) assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that 6.55 out of 26 registrations in the unpublished classification and 2.97 out of 6 registrations in the uncertain classification are actually published (see supplement for details).

@@

After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response (see the supplement for details), we predict that out of a total of 169 included registrations, 103.50 registered studies are published (61.3\%, 95\% CI {[}53.7; 68.3{]}). Our sample contained an almost equal number of manually opened and automatically opened registrations to examine our research question about the consequences of automatically opening registrations after an embargo. As can be seen in Table \ref{tab:table-estimated-nonpublication} manually opened registrations were much more likely to be published than automatically opened registrations, but also somewhat less frequent in the total population of registrations. Multiplying our publication estimates by the estimated number registrations on the OSF before November 2017 that can be classified as an actual research study we find that 5550 registrations are published, and 3994 remain unpublished. Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that 58.2\%, of registrations are published as an article, preprint, thesis, or poster after at least four years.

@@

We see that 85.9\%, 95\% CI {[}77.1; 91.7{]} of all registrations that based on our proxy were classified as manually opened by the researchers have been published. In the remaining 14.1\% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published. This shows that a platform that enables researchers to make their registration public will make studies that would otherwise remain in the file-drawer known to the research community. We estimate that 34.5\%, 95\% CI {[}25; 45.3{]} of automatically opened registrations are published. Consequently, 65.5\% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years. In other words, automatically opening registrations increases our awareness of all studies that have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.

@@

According to the self-reported causes for non-publication researchers shared with us logistical issues are the biggest cause of unpublished studies in our sample. Researchers leave academia and fail to complete a project before their contract ends, move on to a new position with a different research focus, or experience a lack of time to complete this specific project given other responsibilities. Only twice did researchers respond that the project was still in progress, which suggests most projects will not appear in the future, but we did see ongoing research activity in a small number of projects.

@@

When asked why researchers made their OSF project page open, most researchers (18 out of 23) mentioned a motivation to practice open science. Out of 43 responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information stored in the project (15 times), researchers forgot to open it (11 times), researchers were waiting until a project was published (6 times), or they experienced technical issues (4 times). For more details, see the online supplement. Finally, we were interested in how many researchers who registered on the OSF before 2017 were aware of the OSF policy to automatically open all registrations after four years. Although not all researchers answered this question, 24 of the researchers indicated they were aware of this policy, and 14 were not aware of this policy.

@@

Our examination of 169 registrations led to an estimated publication rate of 58.2\% for all registrations on the Open Science framework that were created before November 18, 2017. Extrapolating from our sample to the population of all registrations up to November 2017, we estimate that of the 9544 registered research studies on the OSF that met our inclusion criteria, 3994 remain unpublished. Our study provides an important data point to understand how many studies are performed, but remain unpublished. The possibility that around 41.8\% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research. Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced (\protect\hyperlink{ref-bernal_social_1939}{Bernal, 1939}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}).

The main reason researchers give when asked why their studies remain unpublished are logistical issues related to a lack of time, or responsible researchers moving on to a new job. Better time-management, designing projects from the outset in a way that they can be completed by other team members, or making unfinished projects available to potential collaborators could mitigate these issues. The fact that for 25\% of unpublished studies researchers indicated that the reason that the study remained unpublished is due to the results (e.g., null results or failed replications) is concerning, and considered unacceptable by the general public (\protect\hyperlink{ref-bottesini_what_2022}{Bottesini, Rhemtulla, \& Vazire, 2022}; \protect\hyperlink{ref-pickett_questionable_2017}{Pickett \& Roche, 2017}). It is probable that the absence of these studies contributes to publication bias in the scientific literature. Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report (\protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-nosek_registered_2014}{Nosek \& Lakens, 2014}). If researchers do not report failed replications it is impossible to correct false positive claims in the scientific literature (\protect\hyperlink{ref-schmidt_shall_2009}{Schmidt, 2009}), and if null-results remain unreported effect size estimates in meta-analyses will be inflated (\protect\hyperlink{ref-egger_bias_1997}{Egger, Davey Smith, Schneider, \& Minder, 1997}).

Our estimate has remaining uncertainty as some registrations for which authors did not respond to our email might be classified incorrectly. Furthermore, the estimate is specific to the context of our study, which were all registrations on the OSF created before November 18, 2017. Users of the OSF in these years are early adopters interested in open science practices, and the likelihood they share a study might differ from researchers who do not use the OSF. Our estimate might not generalize to non-registered studies, nor to educational research projects. The estimate might also change over time (e.g., more studies might have remained unpublished during the COVID pandemic). In short, the exact percentage of studies that remain unpublished will be different in other contexts.

At the same time, the factors that cause researchers not to publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts. It should be noted that in fields where results of studies have a high probability of becoming known (e.g., through a requirement to update registrations with the outcome), where researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and where all studies are designed to have a high probability to yield informative results, there might be less reason to be concerned about the number of unpublished studies. Our study demonstrates that the percentage of unpublished studies can be high. Empirically examining the size of the file drawer can determine where there is room for improvement.

\emph{Recommendations for Registries}. We found that the OSF is not only used to (pre)register a study, but also to create a stable archive after a study has been completed. To be able to distinguish these uses of registries, different categories of registrations could be created (e.g., distinguishing `preregistration' from `data archiving', with perhaps an additional category for `educational projects'). It would be useful for meta-scientific research if the API that allows researchers to access data from the registry made it possible to retrieve whether a registration was made public manually or automatically by the OSF. Lastly, the OSF currently displays registrations of separate components of the same project as unique registrations. It would be clearer if one could identify when registrations of components are part of the registration of the overarching project.
